Human Factors Influencing Visual Statistical Inference

### 2013-06-07 sociology_paper.tex
updating experimental table
experimental table updated

There have been \dc{ten} experiments conducted using Amazon's Mechanical Turk~\cite{turk} that are being used to evaluate the the effect of the observer. Table \ref{tbl:visual_stat} summarizes these. Experiments XXX are used to evaluate the effects of demographic factors whethere there is a learning trend. The design of experiment XXX enabled effect of position in the lineup, and the sample of nulls, to be evaluated. Section \ref{sec:factor_performance} describes the factors that may affect the performance of the observer. Section \ref{sec:exp_design} describes the methods used to assess the effects, and Section \ref{sec:result_socio} describes the results.

@@

\begin{table*}[hbtp] 
\caption{Visual test statistics and question asked to the observers to answer while evaluating a lineup } 
\centering 
\begin{tabular}{m{0.5cm}m{2cm}m{3cm}m{7.5cm}} 
\hline\hline 
Case & Statistic & Test Statistic & Lineup question \\ [0.5ex] % inserts table %heading 
\hline 
1  & Box plot & \begin{minipage}[t]{3cm} 	\scalebox{0.45}{\includegraphics{stat_category.pdf}} \end{minipage} & Which set of box plots shows biggest vertical difference 
between group A and B? \\
2 &  Scatter plot & \begin{minipage}[t]{3cm}   \scalebox{0.45}{\includegraphics{stat_beta_k.pdf}}\end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\

@@

Plots to do: for the same signal strength show the proportion correct for scatterplot and boxplot. eg., qplot(effect, ump-visual power, color= plot-type)

>>>>

There have been \dc{ten} experiments conducted using Amazon's Mechanical Turk~\cite{turk} that are being used to evaluate the the effect of the observer. Table \ref{tbl:visual_stat} summarizes these. All of these experiments are used to evaluate the effects of demographic factors. Experiments 5,6 and 7 are used to study learning trend of the observer. The design of experiment 9 enabled effect of position in the lineup, and the sample of nulls, to be evaluated. Section \ref{sec:factor_performance} describes the factors that may affect the performance of the observer. Section \ref{sec:exp_design} describes the methods used to assess the effects, and Section \ref{sec:result_socio} describes the results.

@@

\begin{table*}[hbtp] 
\caption{Visual test statistics and question asked to the observers to answer while evaluating a lineup } 
\centering 
\begin{tabular}{m{.5cm}m{3cm}m{3cm}m{6.5cm}} 
\hline\hline 
Serial & Experiment & Test Statistic & Lineup question \\ [0.5ex] % inserts table %heading 
\hline 
1  & Box plot & \begin{minipage}[t]{3cm} \begin{center}	\scalebox{0.4}{\includegraphics{stat_category.pdf}} \end{center} \end{minipage} & Which set of box plots shows biggest vertical difference 
between group A and B? \\
2 &  Scatter plot & \begin{minipage}[t]{3cm}  \begin{center} \scalebox{0.45}{\includegraphics{stat_beta_k.pdf}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\

  3 & Contaminated plot &\begin{minipage}[t]{3cm} \begin{center} \scalebox{0.45}{\includegraphics{stat_contaminated.pdf}} \end{center} \end{minipage} & Of the scatter plots below which one shows data that has steepest slope? \\  \\ 
  4 & Polar vs Cartesian & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_polar.pdf}} \end{center} \end{minipage} &Which plot is different? \\ 
  5 & Hist vs density & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_density.pdf}} \end{center} \end{minipage} &In which plot is the blue group furthest to the right?\\ 
  6 & Violine vs boxplot & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_violin.pdf}} \end{center} \end{minipage}&  In which plot does the blue group look the most different from  the red group?\\ 
  7 & Group separation & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.4}{\includegraphics{stat_separation.pdf}} \end{center} \end{minipage} &Which of these plots has the most separation between the coloured groups?\\ 
  8 & Sine Illusion & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.28}{\includegraphics{stat_sine.pdf}} \end{center} \end{minipage} & In what picture is the size of the curve most consistent?\\ 
  9 & Gene expression &\begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.45}{\includegraphics{stat_gene.pdf}} \end{center} \end{minipage} & In which of these plots is the green line the steepest, and the spread of the green points relatively small?\\ 
  10 & Test normality & \begin{minipage}[t]{3cm} \begin{center}  \scalebox{0.35}{\includegraphics{stat_normality.pdf}} \end{center} \end{minipage} &Which of these plots is most different from the others?\\

@@

%Plots to do: for the same signal strength show the proportion correct for scatterplot and boxplot. eg., qplot(effect, ump-visual power, color= plot-type)
